Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-07 paper/paper.tex

\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\

>>>>

%\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\
\begin{tabular}{l l l}
apple & itunes & ipad \\
ipod & mac & ios \\
iphone & AAPL & cupertino \\
safari&ilife&iwork \\
garageband&ibook&powerbook \\
itouch&app store&macworld \\
facetime&icloud&mobileme \\
siri&imovie&iphoto \\
quicktime&logic pro&think different
\end{tabular} \\
~\\
